Bioinformatics analysis of whole-genome bisulfite-sequencing data

### 2015-05-02 Rmarkdown/wgbs_bioinformatics_analysis.Rmd
Table captions up top

```{r autosomal_cpg_density_hg19, echo = FALSE, eval = TRUE, message = FALSE, results = "asis"}
library(xtable)
x <- read.table("../data/wgbs_bioinformatics_analysis/CpG_density_hg19.txt",
                header = TRUE, stringsAsFactors = FALSE)
xt <- xtable(x, caption = "Percentage of dinucleotides that are CpGs for each chromosome in the human reference genome (hg19).", label = "tab:cpg_density_hg19")
align(xt) <- rep("c", ncol(x) + 1)
digits(xt) <- 2
print(xt, booktabs = TRUE, comment = FALSE, tabular.environment = "longtable", floating = FALSE, include.rownames = FALSE)
```

@@

>>>>

```{r autosomal_cpg_density_hg19, echo = FALSE, eval = TRUE, message = FALSE, results = "asis"}
library(xtable)
x <- read.table("../data/wgbs_bioinformatics_analysis/CpG_density_hg19.txt",
                header = TRUE, stringsAsFactors = FALSE)
xt <- xtable(x, caption = c("Percentage of dinucleotides that are CpGs for each chromosome in the human reference genome (hg19).", "CpG percentage per chromosome in hg19"), label = "tab:cpg_density_hg19")
align(xt) <- rep("c", ncol(x) + 1)
digits(xt) <- 2
print(xt, booktabs = TRUE, comment = FALSE, tabular.environment = "longtable", floating = FALSE, include.rownames = FALSE, caption.placement = "top")
```

@@

\section{Summary}

__TODO: necessary?__
